A framework for adaptive width control of dense contour-parallel toolpaths in additive manufacturing

### 2019-08-29 6_validation.tex
rename validation to results and discussion
Tims edits to computation time and printing results

\section{Validation}
\jun{section title -> Results?}

@@

\subsubsection{Computational performance}
\cref{computime} plots the computation time for each of the 300 slices against the vertex count of the layer, comparing the uniform technique~\cite{johnson2014clipper} and our framework with the inward distributed scheme. For polygonal shapes with as many as $10^4$ vertices, the computation for both approaches is less than 1 second, with our method being approximately five times that of the uniform technique.

The algorithmic complexity is limited by the generation of the Voronoi Diagram, which is $O(n \log n)$, where $n$ is the number of vertices in the input shape.
The other steps in our framework have a complexity of $O(n)$ or $O(m)$, where $m$ is the number of elements in the ST.
Therefore, the total running time of our algorithm is $O(n \log n)$. Results in \cref{computime} conform that both our framework and the uniform technique have an expected running time of approximately $5 \times 10^{-6} n \log n$ seconds.
% The computation time of our framework is approximately five times that of the uniform technique, which puts it in the same order of magnitude.

% only Moessen reports on computation times, but in a weird manner

\subsection{Printing results}
Test prints were performed on a custom FDM hardware setup, with a standard \SI{0.4}{\milli\meter} nozzle and a filament extrusion drive directly mounted on the print head.
The firmware of the printer employs linear advance: to gain the extra pressure required to change to a wider bead an extra amount of filament is advanced into the physical system between the filament feeder and the nozzle so that we can realize accurate adaptive deposition width control~\cite{tronvoll2019investigating}. \jun{sentence too long}
We set the preferred width to $w^* = \SI{0.6}{\milli\meter}$, to avoid fluttered printing of lines thinner than the nozzle size.
We used a layer thickness of \SI{0.2}{\milli\meter} and a movement speed of \SI{10}{\milli\meter\per\second}.

The prints are shown in \cref{wedge_print} and \cref{prints}.
Because of inaccuracies in the deposition control system some of the prints show defects.
Such defects are less prevalent for the inward distributed beading scheme than the other schemes.
\jun{discuss the positive aspects of the new beading by 2~3 sentences}

>>>>

\section{Results and discussion}

@@

\subsubsection{Computational performance}
\cref{computime} plots the computation time against the vertex count of the layer for the full data set, comparing the uniform technique~\cite{johnson2014clipper} to our framework with the inward distributed scheme.
For polygonal shapes with as many as $10^4$ vertices, the computation for both approaches is less than 1 second, with our method being approximately five times that of the uniform technique.

The algorithmic complexity is limited by the generation of the Voronoi Diagram, which is $O(n \log n)$, where $n$ is the number of vertices in the input shape.
The other steps in our framework have a complexity of $O(m)$, where $m$ is the number of elements in the ST.
Therefore, the total running time of our algorithm is $O(n \log n)$.
Results in \cref{computime} confirm that both our framework and the uniform technique have an expected running time of approximately $5 \times 10^{-6} n \log n$ seconds.

\subsection{Printing results}
Test prints were performed on a custom FDM hardware setup, with a standard \SI{0.4}{\milli\meter} nozzle and a filament extrusion drive directly mounted on the print head.
The firmware of the printer employs \emph{linear advance} for accurately realizing adaptive deposition width:
gaining the extra pressure required to change to a wider bead is realized by 'advancing' an extra amount of filament into the physical system~\cite{tronvoll2019investigating}.
We set the preferred width to $w^* = \SI{0.6}{\milli\meter}$, to avoid fluttered printing of lines thinner than the nozzle size.
We used a layer thickness of \SI{0.2}{\milli\meter} and a movement speed of \SI{10}{\milli\meter\per\second}.

The prints are shown in \cref{wedge_print} and \cref{prints}.
Because of inaccuracies in the deposition control system some of the prints show defects.
Such defects are less prevalent for the inward distributed beading scheme than the other schemes.
The prints which employ the uniform offsets technique clearly show a lot of underfill, which clearly impacts the visual performance of the print.
Moreover, in the case of the regular honeycomb there are several disconnected hexagons, while the whole part is supposed to be a single connected solid.
The difference between the centered and the inward distributed schemes is less pronounced.
We can still see some loosely connected extrusion segments in both, which is attributable to inaccuracies in the extrusion system.
However, the middle of \cref{wedge_print} exhibits more defects in the regions where the centered scheme produces extremal bead widths.
The bottom print shows that the inward distributed beading scheme produces smoother prints with less defects.
